Top Text

### 2022-11-28 Paper.tex
ccommit additions to the introduction

	\section{Introduction}
	During the year of 2022 there has been a massive increase in the popularity of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image. This has led to many different generators being made, which on the one hand has given artist, a person that uses a text-to-image generator to create an image with text, many more options but has also made the landscape difficult to navigate. These new options are great for the field as a whole, however it also means that artists who are not experienced may struggle to find the generator which suits their needs. This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy so we can help give some perspective on which text-to-image generator is best for them.

@@

	Our goal during the course of this reaserch paper is to find out what is the best text-to-image generator, out of the four we chose, for artists who are experienced as well as artists who are not experienced in artificial art generation.

	The best text-to-image generator out of the four we chose will be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which allows the user more freedom to fine-tume their result. Given enough time this will yield a more accurate result.

>>>>

	\section{Introduction}
During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image. This has led to many different generators being made, which on the one hand has given artist, a person that uses a text-to-image generator to create an image with text, many more options but has also made the landscape difficult to navigate with its abundance of choice. These new options are great for the field as a whole, however it also means that artists who are not experienced may struggle to find the generator which suits their needs. This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process so we can help people gain some perspective on which text-to-image generator is best for their needs.

@@

Our goal during the course of this research paper is to find out what is the best text-to-image generator, out of the four we chose, for artists who are experienced as well as artists who are not experienced in artificial art generation.

Another question we take a look at is to find the best technique out of the four applications that we use and then analysing why that technique is so effective for artificial intelligence text-to-image generation. The techniques we will take a look at are latent diffusion, the V4 model, and VOGAN and CLIP.

The text-to-image generators we will be testing during the course of this paper are: Stable diffusion, Midjourney, DallE and Dream by Wombo. Stable diffusion was released in 2022 and makes use of the ai text-to-image synthesis technique known as latent diffusion. Midjourney which is currently in open beta and also makes use of latent diffusion to generate its images. DallE was released in January of 2021 and makes use of the V4 model to generate its images. Finally is dream by Wombo which was released in late 2021 and makes use of a combination of VOGAN and CLIP for text-to-image generation.

The best text-to-image generator out of the four we chose will be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which allows the user more freedom to fine-tune their result. Given enough time this will yield a more accurate result.
